Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-09 paper/paper.tex
discussing mutational fuzzers + dos2unix on references.bib

\Mar{------------ estou aqui -M}

\Fix{quick on mutational fuzzers}

Coverage-based fuzzers like American Fuzz Loop (AFL)~\cite{afl} and
libfuzzer~\cite{libfuzzer} run tests inputs in coverage-instrumented
versions of the program under testing. The typical approach to input
generation of this kind of fuzzer is evolutionary--they try to
minimize the distances to still uncovered branches of the
program. AFL, for instance, takes the instrumented program binary and
one input seed and produces on output crash inputs. Considering our
context of application, we needed to build one runtime engine to
collect coverage information for fuzzing; we chose v8. (There are
options in LLVM clang for that~\cite{libfuzzer}.)  Unfortunately, we
found that most of the inputs produced violate the JS grammar and the
fuzzing task can take days even when considering one seed. That
happens because the entire decision tree of the engine is explored,
including the branches associated with the lexer and parser. For this
reason, Google promotes the creation of fuzz targets associated with
specific program functions. Although that approach has shown very
effective, it requires domain knowledge to create the calling context
for the fuzz target. For those reason, coverage-based fuzzers were not
considered in this study.

>>>>

Mutational fuzzers can be either white-box (coverage-based) or
black-box. Coverage-based fuzzers like American Fuzz Loop
(AFL)~\cite{afl} and libfuzzer~\cite{libfuzzer} run tests inputs
against instrumented versions of the program under testing with the
typical goal of finding univeral errors like crashes and buffer
overflows. The instrumentation adds code to collect coverage and
monitor properties\footnote{ There are options in the clang toolchain
  to build programs with fuzzing
  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
  for property checking~\cite{clang-documentation}.}. The typical
approach to input generation is evolutionary--these fuzzers try to
minimize the distances to still-uncovered branches of the
program. AFL, for instance, takes the instrumented program binary
(say, a JS engine) and one seed input to that program (say, a JS
program) and produces on output fault-revealing inputs. Considering
our context of application, we needed to instrument one runtime engine
for fuzzing; we chose v8 for this. Unfortunately, we found that most
of the inputs produced by AFL violate the JS grammar. Furthermore, the
fuzzing task took days even when considering only one seed and there
is no simple way to guide the exploration. That happens because the
fuzzer aims to explore the entire decision tree induced from the
engine's main function, including the branches associated with the
lexer and the parser. For that reasons, coverage-based fuzzers were
not considered in this study. It is worth mentioning that Google
mitigates that problem by promoting developers to create fuzz targets
for specific program functions\Fix{cite}. Although that approach has
shown very effective, it requires domain knowledge to create the
calling context to invoke the fuzz target.
